---
title: "p8510_hw1_ly2496"
author: Ling Yi
date: "9/15/2020"
output: github_document
---

This is my solution to hw1

```{r}
library(tidyverse)
```


##Problem 1

Create a data frame for the specified elements

```{r}

prob1_df <- 
  tibble (
    samp = rnorm(10),
    sampe_gt_0 = samp >0, 
    char_vec = c("a", "b", "c", "d", "e", "f", "G", "h", "I", "j"),
    factor_vec = factor(c("low", "low", "low", "med", "med", "med", "med", "high", "high", "high"))
 
 ) 

```


Take the mean of each variable in the data frame


```{r}

mean(pull(prob1_df, samp))
mean(pull(prob1_df, sampe_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))

```

I can take the mean of numeric or logical variables, but not character or vectors. 
For the logical vector, R is conducting variable coercion (taking those that is logical and turning them into the numbers and then taking the mean of it)


```{r}

as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, sampe_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))

```

```{r}
as.numeric(pull(prob1_df, samp)) * pull(prob1_df, samp)
as.factor (pull(prob1_df, samp)) * pull(prob1_df, samp)
##Returned an error message stating not meaningful for vectors 
as.factor(pull(prob1_df, sampe_gt_0))
as.numeric(pull(prob1_df, sampe_gt_0)) *pull(prob1_df, samp)

```
##Problem 2

```{r}
install.packages("palmerpenguins")

data("penguins", package = "palmerpenguins")

```

**descirption of the penguins data set using inline R code**


This code `r summary(penguins)` will be used to get the names and the values for each variable in the dataset. 
This code `r nrow(penguins)` and `r ncol(penguins)` will be used to get the total number of rows and columns in the dataset respectively. 
This code `r mean(penguins$lipper_length_mm)` will be used to get the mean flipper length. 


**creating a scatterplot of the flipper_length_mm (y) vs bill_length_mm (x)**

```{r}
library(ggplot2)

ggplot(data = penguins, mapping = aes(x = bill_length_mm, y=flipper_length_mm, color=species)) + geom_point() +
labs(x = "Bill Length (mm)", y = "Flipper Length (mm)")+
  ggtitle("Plot of Flipper and Bill (mm)")
```
**exporting the plot to project directory**

```{r}
ggsave("Scatter_plot_flipper_bill.pdf", height = 4, width = 6)
)
```





